### 2014-08-19 fundamentals/intro.tex
adds some more intro citations and content

In nuclear fuel cycle simulation, it is necessary to calculate and optimize 
nuclear process physics, facility deployment, and material routing in order to 
capture overall fuel cycle performance metrics.

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to very high-fidelity industrial 
models.

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform.

@@

Simulators drive R\&D by calculating metrics that can be compared accross fuel 
cycles.

Previous simulators have been static or dynamic. Some have been discrete while 
others have been fleet-based. Some have captured regional behavior, material 
isotopics, transmutation detail, etc. Indeed, some tools have attempted 
agent-based functionality.

Historically, the national laboratories have driven development and regulated 
the use of their own tools (cite VISION, DANESS, NFCSim, etc.), while 
universities and industry have simultaneously developed tools of their own as 
well.

The Cyclus code arose out of the GENIUSv2 code. That software itself was the 
result of lessons-learned from an LDRD project at INL called GENIUSv1.

>>>>

In order to characterize performance metrics, nuclear fuel cycle analysis 
requires calculation and optimization of myriad physical, nuclear, chemical, 
industrial, and political phenomena. Furthermore, complex systems such as 
nuclear process physics, facility deployment, and material routing each each 
must be modeled simultaneously for even the simplest of nuclear fuel cycle 
simulations.

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to very high-fidelity 
industrial models. To date, current tools are either static, fleet-based, or 
privately distributed. An alternative to these approaches is a dynamic, 
agent-based simulator with an open platform.

Modern insight indicates that dynamic nuclear fuel cycle analysis more 
realistically supports a broader range of simulation goals than static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the greater field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{thatpapermattsent}. Finally, 
openness allows cross-institutional collaboration, increases code robustness, 
and enables the cultivation of an ecosystem of calculation options, 
\cite{softwarecarpentryresource}.

Myriad challenges in nuclear fuel cycle analysis could be 
addressed with an agent-based framework for simulation and tracking of 
transformation and trade of resources between facilities within institutions 
and regions.

@@

Simulators drive \gls{RDD} by calculating metrics that can be compared among fuel 
cycles. Examples include measures of economic feasibility (i.e., \gls{LCOE}), 
proliferation risk (i.e., total separated Pu), and environmental performance 
(i.e., waste volume).

Methods for calculating those metrics vary among simulators. Some model the fuel cycle at static equillibrium, while others 
capture fuel cycle dynamics.  Similarly, while some simulators discretely model 
material and and facilities, others track streams of materials and 
fleets of facilities in an aggregated fashion. Depending on their intended use, 
simulators often model some aspect of the fuel cycle in great detail. For this 
reason, simulators specialize in economics, material isotopics, or 
transmutation detail, where others do not. Some tools have even attempted 
agent-based functionality.

Historically, the national laboratories have driven development and regulated 
the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{modeling_yacout_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}, while universities and industry have 
simultaneously developed tools of their own as well, such as 
\gls{CAFCA}\cite{guerin_benchmark_2006}.

The Cyclus code arose out of the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
itself was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
captured regional behaviors in fuel cycle scenarios.
